REVISITING SEMI-CONTINUOUS HIDDEN MARKOV MODELS

### 2011-09-27 misc/papers/icassp12_tied/icassp12.tex
git-svn-id: https://svn.code.sf.net/p/kaldi/code/sandbox/discrim@522 5e6a8d80-dfce-4ca6-a32a-6e07a63d50c8

\subsection{Resource Management}
For the RM data set, we train on the speaker independent training and development 
set (about 4000 utterances) and test on the six DARPA test runs Mar and Oct '87,
Feb and Oct '89, Feb '91 and Sep '92 (about 1500 utterances total).  The parameters 
were tuned to the test set.
%
\begin{itemize}
\item
  {\em cont}: continuous triphone system using 9011 diagonal covariance
  Gaussians in 1480 tree leaves
\item
  {\em semi}: semi-continuous triphone system using 768 full covariance
  Gaussians in 2500 tree leaves, but no smoothing (explanations below).
\item
  {\em 2lvl}: two-level tree based semi-continuous triphone system using
  3072 full covariance Gaussians in 208 codebooks ($4/14.7/141$ min/average/max
  components), 2500 tree leaves, $\rho = 35$ and $\varrho = 0.2$.
\item
  {\em sgmm}: subspace Gaussian mixture model triphone system using a 400 
  full-covariance Gaussian background model and 2016 tree leaves.
\end{itemize}

@@

Keeping the number of codebooks and leaves as well as the smoothing parameters
$rho$ and $\varrho$ of {\em 2lvl} constant, we experiment with the number of
Gaussians and type of covariance; the results are displayed in 
Tab.~\ref{tab:rm_diagfull}.
Interestingly, the full covariances make a strong difference: Using the same
number of Gaussians, full covariances lead to a significant improvement.
On the other hand, a substantial increase of the number of diagonal Gaussians 
leads to a similar performance as the regular continuous system.
%
Another observation from Tab.~\ref{tab:rm_diagfull} is that the smoothing
parameters need to be carefully calibrated. While the inter-iteration smoothing
helps in most cases, the intra-iteration smoothing coefficient $\rho$ strongly
depends on the type and number of Gaussians, which is due to the direct influence
of $\rho$ in Eq.~\ref{eq:intra}.

@@

\bibliographystyle{IEEEbib}
\bibliography{refs-eig,refs}

>>>>

\subsection{Resource Management}
For the RM data set, we train on the speaker independent training and development 
set (about 4000 utterances) and test on the six DARPA test runs Mar and Oct '87,
Feb and Oct '89, Feb '91 and Sep '92 (about 1500 utterances total).  The parameters 
were tuned to the test set.
%
\begin{itemize}
\item
  {\em cont}: continuous triphone system using 9011 diagonal covariance
  Gaussians in 1480 tree leaves
\item
  {\em semi}: semi-continuous triphone system using 768 full covariance
  Gaussians in 2500 tree leaves, no smoothing (explanations later).
\item
  {\em 2lvl}: two-level tree based semi-continuous triphone system using
  3072 full covariance Gaussians in 208 codebooks ($4/14.7/141$ min/average/max
  components), 2500 tree leaves, $\rho = 35$ and $\varrho = 0.2$.
\item
  {\em sgmm}: subspace Gaussian mixture model triphone system using a 400 
  full-covariance Gaussian background model and 2016 tree leaves.
\end{itemize}

@@

Keeping the number of codebooks and leaves as well as the smoothing parameters
$rho$ and $\varrho$ of {\em 2lvl} constant, we experiment with the number of
Gaussians and type of covariance; the results are displayed in 
Tab.~\ref{tab:rm_diagfull}.
Interestingly, the full covariances make a strong difference: Using the same
number of Gaussians, full covariances lead to a significant improvement.
On the other hand, a substantial increase of the number of diagonal Gaussians 
leads to a similar performance as the regular continuous system.
%
Another observation from Tab.~\ref{tab:rm_diagfull} is that the smoothing
parameters need to be carefully calibrated. While the inter-iteration smoothing
helps in most cases, the intra-iteration smoothing coefficient $\rho$ strongly
depends on the type and number of Gaussians, which is due to the direct influence
of $\rho$ on the counts in Eq.~\ref{eq:intra}.

@@

% Korbinian: We might need that ;)
%\footnotesize
\bibliographystyle{IEEEbib}
\bibliography{refs-eig,refs}
